---
title: "Sponsored Project Proposal Text Mining"
format: html
editor: visual
self-contained: true
execute: 
  echo: true
  message: false
  warning: false
---

# Text Mining of Proposals for DEI Flags

```{r}
library(tidytext)
library(pdftools)
#library(officer)
library(readtext)
library(tidyverse)
library(gmRi)
```

## Red Flag Words

The following shortlist covers words said to be drawiung scrutiny in NSF proposals.

```{r}
nsf_keywords <- c(
  "implicit bias",
  "inclusion",
  "inclusive",
  "inclusivity",
  "inequitites",
  "institutional",
  "intersectional",
  "male dominated",
  "marginalized",
  "minority",
  "multicultural",
  "oppression",
  "polarization",
  "racially",
  "advocacy",
  "antiracist",
  "barrier",
  "biases",
  "cultural relevance",
  "disability",
  "diverse backgrounds",
  "diversity",
  "diversified",
  "ethinicity",
  "excluded",
  "exclusion",
  "equity",
  "female",
  "gender",
  "hate speech",
  "historically",
  "segregation",
  "socioeconomic",
  "systemic", 
  "trauma", 
  "underrepresented", 
  "underserved", 
  "victims", 
  "women"
)
```

## DEI Word Categories

The insanse document with Ted Cruz's name on it has keywords by category:

```{r}
status_keywords <- c(
  "ACTIVISM", "ACTIVIST", "ACTIVISTS", "ADVOCACY", "ADVOCATE", "ADVOCATES", "AFFIRMATIVE ACTION", "BIAS TOWARD","BIAS TOWARDS", "BIASED", "BIASED TOWARD", "BIASED TOWARDS", "BIASES", "BIASES TOWARD", "BIASES TOWARDS", "DE COLONIZATION", "DE COLONIZE", "DE COLONIZED", "DE COLONIZING", "DE SEGREGATE", "DE SEGREGATED", "DE SEGREGATES", "DE SEGREGATION", "DECOLONIZATION", "DECOLONIZE", "DECOLONIZED", "DECOLONIZING", "DESEGREGATE", "DESEGREGATED", "DESEGREGATES", "DESEGREGATION", "DISCRIMINATE", "DISCRIMINATED", "DISCRIMINATION", "DISCRIMINATORY", "DIVISIVENESS", "EXCLUDED", "EXCLUSION", "EXCLUSIVE", "FEEL SEEN AND HEARD",
"HATE SPEECH", "HISTORICALLY", "IMPLICIT BIAS", "IMPLICIT BIASES", "INJUSTICE", "INJUSTICES", "INSTITUTIONAL", "INSTITUTIONALIZE", "INSTITUTIONALIZED", "INSTITUTIONALLY", "INTERGENERATIONAL TRAUMA", "INTERSECTIONAL", "INTERSECTIONALITY", "MARGINALIZATION", "MARGINALIZE", "MARGINALIZED", "MICRO AGGRESSION", "MICRO AGGRESSIONS", "MICRO AGGRESSIVE", "MICRO AGGRESSIVENESS", "MICROAGGRESSION", "MICROAGGRESSIONS", "MICROAGGRESSIVE", "MICROAGGRESSIVENESS", "MINORITIES", "MINORITY", "OPPRESSED", "OPPRESSIVE",
"OPPRESSIVENESS", "OPPRESSION", "POLARIZATION", "POLARIZE", "POLITICIZATION", "POLITICIZE", "POLITICAL", "PREJUDICE", "PREJUDICES", "PRIVILEGE", "PRIVILEGED", "PRIVILEGES", "REPARATION", "REPARATIONS", "SEGREGATED", "SEGREGATION", "SOCIO ECONOMIC", "SOCIOECONOMIC", "STATUS", "STATUSES", "STEREOTYPE", "STEREOTYPES", "STEREOTYPICAL", "STEREOTYPING", "SYSTEM OF OPPRESSION", "SYSTEMATIC OPPRESSION", "SYSTEMATICALLY OPPRESSED", "SYSTEMIC",
"SYSTEMIC OPPRESSION", "SYSTEMICAL", "SYSTEMICALLY", "SYSTEMICALLY OPPRESSED", "SYSTEMS OF OPPRESSION", "SYSTEMS OF POWER", "TRAUMA", "TRAUMATIC", "UNDER APPRECIATED", "UNDER APPRECIATION", "UNDER PRIVILEGE", "UNDER PRIVILEGED", "UNDER REPRESENTATION", "UNDER REPRESENTED", "UNDER SERVED", "UNDER SERVING", "UNDER VALUED", "UNDER VALUING", "UNDERAPPRECIATED", "UNDERAPPRECIATION", "UNDERPRIVILEGE", "UNDERPRIVILEGED",
"UNDERREPRESENTATION", "UNDERREPRESENTED", "UNDERSERVED", "UNDERSERVING", "UNDERVALUED", "UNDERVALUING", "UNJUST", "VICTIM", "VICTIMHOOD", "VICTIMIZED", "VICTIMS", "VOICES ARE ACKNOWLEDGED", "VOICES HEARD", "VOICES MATTER", "UNEQUAL OPPORTUNITIES", "UNEQUAL OPPORTUNITY", "SAFE SPACE", "SAFE SPACES", "SENSE OF BELONGING", "SENSE OF BELONGINGNESS", "WELCOMING ENVIRONMENT", "BARRIER", "BARRIERS", "DISABILITIES", "DISABILITY", "ALLY", "ALLYSHIP")
```

```{r}
social_justice_keywords <- c("ADVANCE DIVERSITY", "ADVANCE INCLUSIVITY", "ADVANCE THE DIVERSITY", "ADVANCING DIVERSITY", "ADVANCING INCLUSIVE", "ALLIANCE FOR DIVERSITY", "BACKGROUND INCLUSIVITY", "BI CULTURAL", "BICULTURAL", "BLACK CULTURAL", "BLACK CULTURE", "BLACK CULTURES", "BROADEN DIVERSITY", "BROADEN THE DIVERSITY", "COMMITMENT TO DIVERSITY", "COMMUNITY DIVERSITY", "COMMUNITY EQUITY", "COMMUNITY INCLUSIVITY", "CULTURAL ACTIVISM", "CULTURAL ACTIVIST", "CULTURAL ACTIVISTS", "CULTURAL ADVOCACY", "CULTURAL ADVOCATE", "CULTURAL AND ETHNIC", "CULTURAL AND RACIAL", "CULTURAL APPROPRIATION", "CULTURAL APPROPRIATIONS", "CULTURAL BIAS", "CULTURAL COMPETENCY", "CULTURAL CONNECTIONS", "CULTURAL DIFFERENCES", "CULTURAL HERITAGE", "CULTURAL HUMILITY", "CULTURAL INEQUALITIES", "CULTURAL INEQUALITY", "CULTURAL INEQUITIES", "CULTURAL INEQUITY", "CULTURAL INJUSTICE", "CULTURAL INJUSTICES", "CULTURAL JUSTICE", "CULTURAL RELEVANCE", "CULTURAL SEGREGATION", "CULTURALLY ATTUNED", "CULTURALLY BIASED", "CULTURALLY RESPONSIVE", "CULTURALLY SENSITIVE", "CULTURALLY SUSTAINABLE", "CULTURALLY SUSTAINING", "CULTURE AND ETHNICITY", "CULTURE AND RACE", "CULTURES AND ETHNICITIES", "CULTURES AND RACES", "DEI", "DEIJ", "DIVERSE BACKGROUND", "DIVERSE BACKGROUNDS", "DIVERSE COMMUNITIES", "DIVERSE COMMUNITY", "DIVERSE GROUP", "DIVERSE GROUPS", "DIVERSE INDIVIDUAL", "DIVERSE INDIVIDUALS", "DIVERSE STATUS", "DIVERSE STATUSES", "DIVERSE VOICES", "DIVERSIFIED", "DIVERSIFY", "DIVERSIFYING", "DIVERSITY AND EQUITY", "DIVERSITY AND INCLUSION", "DIVERSITY AND INCLUSIVITY", "DIVERSITY AWARENESS", "DIVERSITY EQUITY", "EMPHASIS ON DIVERSITY", "EMPHASIZE DIVERSITY", "EMPHASIZING DIVERSITY", "ENCOURAGE DIVERSITY", "ENCOURAGING DIVERSITY", "ENHANCE DIVERSITY", "ENHANCE THE DIVERSITY", "ENHANCING DIVERSITY", "EQUAL OPPORTUNITIES", "EQUAL OPPORTUNITY", "EQUALITIES", "EQUALITY", "EQUITABLE", "EQUITABLE AND INCLUSIVE", "EQUITIES", "EQUITY", "ETHNIC AND CULTURAL", "ETHNIC CULTURAL", "ETHNIC CULTURE", "ETHNIC CULTURES", "ETHNIC DIVERSITY", "ETHNIC EQUITY", "ETHNICITIES AND CULTURES", "ETHNICITY AND CULTURE", "FOSTER DIVERSITY", "FOSTERING DIVERSITY", "FOSTERING INCLUSIVE", "FOSTERING INCLUSIVITY", "FOSTERING THE DIVERSITY", "GROUP EQUITY", "GROUP INCLUSIVITY", "HISPANIC CULTURAL", "HISPANIC CULTURE", "HISPANIC CULTURES", "INCLUSION", "INCLUSIVE", "INCLUSIVE LANGUAGE", "INCLUSIVENESS", "INCLUSIVITY", "INCLUSIVITY AND DIVERSITY", "INCREASE DIVERSITY",
"INCREASE THE DIVERSITY", "INCREASES DIVERSITY", "INCREASES THE DIVERSITY", "INCREASING DIVERSITY", "INCREASING THE DIVERSITY", "INDIGENOUS CULTURAL", "INDIGENOUS CULTURE", "INDIGENOUS CULTURES", "INEQUALITIES", "INEQUALITY", "INEQUITABLE", "INEQUITIES", "INEQUITY", "INTER CULTURAL", "INTER CULTURALLY", "INTERCULTURAL", "INTERCULTURALLY", "LACK OF DIVERSITY", "LATINX CULTURAL", "LATINX CULTURE", "LATINX CULTURES", "MULTI CULTURAL", "MULTI CULTURALLY", "MULTICULTURAL", "MULTICULTURALLY", "PROMOTE DIVERSITY", "PROMOTING DIVERSITY", "SEGREGATED CULTURES", "SOCIAL ACTIVISM", "SOCIAL ACTIVIST", "SOCIAL ACTIVISTS", "SOCIAL ADVOCACY", "SOCIAL ADVOCATE", "SOCIAL BIAS", "SOCIAL BIASES", "SOCIAL INEQUALITIES", "SOCIAL INEQUALITY", "SOCIAL INEQUITIES", "SOCIAL INEQUITY", "SOCIAL INJUSTICE", "SOCIAL INJUSTICES", "SOCIAL JUSTICE", "SOCIAL JUSTICE ACTIVISM", "SOCIAL JUSTICE ADVOCACY", "SOCIAL JUSTICE ADVOCATE", "SOCIALLY BIASED", "SOCIO CULTURAL", "SOCIO CULTURALLY", "SOCIOCULTURAL", "SOCIOCULTURALLY", "STRUCTURAL INEQUALITY", "STRUCTURAL INEQUITY", "SUPPORT DIVERSITY", "SUPPORTING DIVERSITY", "TRANS CULTURAL", "TRANSCULTURAL", "SOCIALLY RELEVANT", "CULTURALLY RELEVANT")
```

```{r}
gender_keywords <- c(
  "BIGOT", "BIGOTRY", "BLACK FEMALE", "BLACK FEMALES", "BLACK MALE", "BLACK MALES", "BLACK MEN", "BLACK WOMEN", "CISGENDER", "CISNORMATIVE", "CISNORMATIVITY", "COLORED FEMALE", "COLORED FEMALES", "COLORED MALE", "COLORED MALES", "COLORED MEN", "COLORED WOMEN", "FEMALE", "FEMALE VOICES", "FEMALES", "FEMININITY", "FEMINISM", "FEMINIST", "FEMINISTIC", "FLUID IDENTITY", "GENDER", "GENDER ACCEPTANCE", "GENDER AFFIRMATION", "GENDER AFFIRMING", "GENDER AND SEXUAL", "GENDER APPRECIATION", "GENDER BASED", "GENDER BINARY", "GENDER DISCRIMINATION", "GENDER DISPARITIES", "GENDER DISPARITY", "GENDER DIVERSITY", "GENDER DYSMORPHIA", "GENDER
DYSPHORIA", "GENDER FLUID", "GENDER FLUIDITY", "GENDER IDENTITY", "GENDER IDEOLOGY", "GENDER INCLUSIVE", "GENDER INCLUSIVITY", "GENDER MARGINALIZED", "GENDER MINORITIES", "GENDER MINORITY", "GENDER NEURAL", "GENDER NON BINARY", "GENDER NON CONFORMING", "GENDER NONBINARY", "GENDER NONCONFORMING", "GENDER OPPRESSION", "GENDER PREFERENCE", "GENDER PREFERENCES", "GENDER SPECTRUM", "GENDER STEREOTYPES", "GENDER TRANSITION", "GENDER TRANSITIONING", "GENDER TYPICAL", "GENDERS", "HETEROSEXUAL", "HISPANIC FEMALE", "HISPANIC FEMALES", "HISPANIC MALE", "HISPANIC MALES", "HISPANIC MEN", "HISPANIC WOMEN", "HISTORICALLY MALE", "INDIGENOUS FEMALE", "INDIGENOUS FEMALES", "INDIGENOUS MALE", "INDIGENOUS MALES", "INDIGENOUS MEN", "INDIGENOUS WOMEN", "INTERSECTIONAL FEMINISM", "LATINA FEMALE", "LATINA FEMALES", "LATINA MALE", "LATINA MALES", "LATINA MEN", "LATINA WOMEN", "LATINX FEMALE", "LATINX FEMALES", "LATINX MALE", "LATINX MALES", "LATINX MEN", "LATINX WOMEN", "LGBT", "LGBTQ", "LGBTQ+", "LGBTQIA", "MALE DOMINANT", "MALE DOMINATED", "MASCULINE", "MASCULINITY", "MIS GENDER", "MISGENDER", "MISOGYNISTIC", "MISOGYNY", "NON BINARY", "NON BINARY GENDER", "NON CONFORMING GENDER", "NONBINARY", "NONBINARY GENDER", "NONCONFORMING GENDER", "OPPRESSED GENDER", "OPPRESSED GENDERS", "OPPRESSED SEXUALITIES", "PANSEXUAL", "PREDOMINATELY MALE", "PREFERRED GENDER", "PREFERRED IDENTITY", "PREFERRED SEX", "PRIMARILY MALE", "PRONOUN", "PRONOUNS", "QUEER THEORY", "SELF IDENTIFY", "SEX CHANGE", "SEX PREFERENCE", "SEX TRANSITION", "SEXISM", "SEXIST", "SEXUAL DISCRIMINATION", "SEXUAL DISPARITIES", "SEXUAL DISPARITY", "SEXUAL IDENTITY", "SEXUAL MINORITIES", "SEXUAL MINORITY", "SEXUAL PREFERENCE", "SEXUAL PREFERENCES", "SEXUALITIES", "SEXUALITY", "STRAIGHT WHITE", "TOXIC MASCULINITY", "TRANSGENDER", "TRANSGENDERISM", "TRANSITIONING GENDER", "TRANSITIONING SEX", "TRANSJUSTICE", "TRANSPHOBIA", "TRANSPHOBIC", "UNDERREPRESENTED GENDER", "VOICES OF WOMEN", "WHITE FEMALE", "WHITE FEMALES", "WHITE MALE", "WHITE MALES", "WHITE MEN", "WHITE WOMEN", "WOMEN", "WOMEN AND GENDER", "WOMEN AND UNDERREPRESENTED", "WOMENUNDERREPRESENTED"
)
```

```{r}
race_keywords <- c("ANTI BLACK", "ANTI BLACK RACISM", "ANTI RACISM", "ANTI RACIST", "ANTI WHITE", "ANTIBLACK", "ANTIBLACK RACISM", "ANTIRACISM", "ANTIRACIST", "ANTIWHITE", "BIPOC", "BIPOCX", "BLACK AND LATINX", "BLACK COMMUNITIES", "BLACK COMMUNITY", "BLACK INDIGENOUS AND LATINX", "BLACK INDIGENOUS AND OTHER", "BLACK INDIGENOUS LATINX", "BLACK INDIGENOUS OTHER", "BLACK INDIVIDUAL", "BLACK INDIVIDUALS", "BLACK INTELLECTUALISM", "BLACK LIVES MATTER", "BLACK MINORITIES", "BLACK MINORITY", "BLACK PEOPLE", "BLACK PERSON", "BLACK THOUGHT", "BLACK VOICES", "BLACKNESS", "COLORED COMMUNITIES", "COLORED COMMUNITY", "COLORED INDIVIDUAL", "COLORED INDIVIDUALS", "COLORED MINORITIES", "COLORED MINORITY", "COLORED PEOPLE", "COLORED PERSON", "COLORED VOICES", "CRITICAL RACE THEORY", "ETHNIC AND RACIAL", "ETHNIC BIAS", "ETHNIC COMMUNITIES", "ETHNIC COMMUNITY", "ETHNIC IDENTITIES", "ETHNIC IDENTITY", "ETHNIC INDIVIDUAL", "ETHNIC INDIVIDUALS", "ETHNIC MINORITIES", "ETHNIC MINORITY", "ETHNIC PEOPLE", "ETHNIC PERSON", "ETHNIC RACISM", "ETHNIC SEGREGATION", "ETHNIC VOICES", "ETHNICAL RACISM", "ETHNICITIES AND RACES", "ETHNICITY", "ETHNICITY AND RACE", "HISPANIC COMMUNITIES", "HISPANIC COMMUNITY", "HISPANIC INDIVIDUAL", "HISPANIC INDIVIDUALS", "HISPANIC MINORITIES", "HISPANIC MINORITY", "HISPANIC PEOPLE", "HISPANIC PERSON", "HISPANIC VOICES", "HISTORICAL RACISM", "HISTORICALLY RACIST", "HISTORICALLY WHITE", "INDIGENOUS COMMUNITIES", "INDIGENOUS COMMUNITY", "INDIGENOUS INDIVIDUAL", "INDIGENOUS INDIVIDUALS", "INDIGENOUS MINORITIES", "INDIGENOUS MINORITY", "INDIGENOUS PEOPLE", "INDIGENOUS PERSON", "INDIGENOUS VOICES", "INSTITUTIONAL RACISM", "INSTITUTIONALIZED RACISM", "INSTITUTIONALLY RACIST", "INTER RACIAL", "INTER RACIALLY", "INTERRACIAL", "INTERRACIALLY", "LATINA COMMUNITIES", "LATINA COMMUNITY", "LATINA INDIVIDUAL", "LATINA INDIVIDUALS", "LATINA MINORITIES", "LATINA MINORITY", "LATINA PEOPLE", "LATINA PERSON", "LATINA VOICES", "LATINX COMMUNITIES", "LATINX COMMUNITY", "LATINX INDIVIDUAL", "LATINX INDIVIDUALS", "LATINX MINORITIES", "LATINX MINORITY", "LATINX PEOPLE", "LATINX PERSON", "LATINX VOICES", "MULTI ETHNIC", "MULTI ETHNICALLY", "MULTIETHNIC", "MULTIETHNICALLY", "NON BLACK", "NON WHITE", "NONBLACK", "NONWHITE", "PEOPLE OF COLOR", "POC", "POCX", "PREDOMINATELY WHITE", "PRIMARILY WHITE", "PRIVILEGED WHITE", "PRO BLACK", "PRO WHITE", "PROBLACK", "PROWHITE", "RACE AND CULTURE", "RACE AND ETHNICITY", "RACE BASED", "RACEBASED", "RACES AND CULTURES", "RACES AND ETHNICITIES", "RACIAL", "RACIAL AND
CULTURAL", "RACIAL AND ETHNIC", "RACIAL BIAS", "RACIAL BIASES", "RACIAL DISPARITIES", "RACIAL DISPARITY", "RACIAL DIVERSITY", "RACIAL IDENTITY", "RACIAL INEQUALITIES", "RACIAL INEQUALITY", "RACIAL INEQUITIES", "RACIAL INEQUITY", "RACIAL INJUSTICE", "RACIAL INJUSTICES", "RACIAL JUSTICE", "RACIAL MINORITIES", "RACIAL MINORITY", "RACIAL OPPRESSION", "RACIAL PREJUDICE", "RACIAL PREJUDICES", "RACIAL SEGREGATION", "RACIAL SOCIALIZATION", "RACIAL
SOLIDARITY", "RACIAL STEREOTYPES", "RACIAL VIOLENCE", "RACIALLY", "RACIALLY AND CULTURALLY", "RACIALLY BIAS", "RACIALLY BIASED", "RACIALLY OPPRESSED", "RACISM", "RACIST", "SEGREGATED ETHNICITIES", "SEGREGATED ETHNICITY", "SEGREGATED RACE", "SEGREGATED RACES", "STRUCTURAL RACISM", "STRUCTURALLY RACIST", "SYSTEMIC RACISM", "SYSTEMICALLY RACIST", "TOKENISTIC", "TOKENSIM", "TRANS ETHNIC", "TRANSETHNIC", "WHITE COLONIALISM", "WHITE COLONIZATION", "WHITE COLONIZER", "WHITE COLONIZERS", "WHITE FRAGILITY", "WHITE HISTORICALLY", "WHITE NATIONALISM", "WHITE NATIONALIST", "WHITE PEOPLE", "WHITE PERSON", "WHITE PRIVILEGE", "WHITE SERVING", "WHITE SUPREMACY", "WHITENESS")
```

```{r}
env_justice_keywords <- c("CLIMATE ACTION", "CLIMATE CONSCIOUS", "CLIMATE CONSCIOUSNESS", "CLIMATE EQUALITY", "CLIMATE EQUITY","CLIMATE JUSTICE", "CLIMATE RESEARCH", "ECO CULTURAL", "ECOCULTURAL", "ENVIRONMENT CONSCIOUS","ENVIRONMENT CONSCIOUSNESS", "ENVIRONMENTAL CONSCIOUS", "ENVIRONMENTAL CONSCIOUSNESS", "ENVIRONMENTAL EQUALITY", "ENVIRONMENTAL EQUITY", "ENVIRONMENTAL GOVERNANCE", "ENVIRONMENTAL JUSTICE", "ENVIRONMENTAL SOCIAL", "ENVIRONMENTALGOVERNANCE", "ENVIRONMENTALLY CONSCIOUS", "ENVIRONMENTALSOCIAL", "ESG", "ESG EFFORT", "ESG EFFORTS", "ESG INITIATIVE", "ESG INITIATIVES", "GREEN NEW DEAL", "NET ZERO", "NETZERO", "SOCIAL ENVIRONMENTAL", "SOCIALENVIRONMENTAL", "CLIMATE INJUSTICE", "CLIMATE JUSTICES", "CLIMATE INJUSTICES", "CLIMATE CHANGE", "GREEN INFRASTRUCTURE", "GREEN SOCIETY", "CLEAN ENERGY")
```

## Load Proposals

We have two folders of proposals, those that have been awarded and those that are pending.

```{r}
# Path to awarded federal proposals
awarded <- cs_path("root", "Awarded Federal Proposals")
pending <- cs_path("root", "Pending Federal Proposals")

# awarded proposals
awarded_proposals <- setNames(
  list.files(awarded, full.names = T) %>% as.list(),
  list.files(awarded))


# Pending proposals
pending_proposals <- setNames(
  list.files(pending, full.names = T) %>% as.list(),
  list.files(pending))


```

### Keyword Search Function(s)

```{r}

# Function to extract text from different file types
extract_text <- function(file_path) {
  if (grepl("\\.pdf$", file_path, ignore.case = TRUE)) {
    return(paste(pdf_text(file_path), collapse = " "))  # Merge PDF pages into one string
  } else if (grepl("\\.docx$", file_path, ignore.case = TRUE)) {
    return(paste(readtext(file_path)$text, collapse = " "))  # Read DOCX text
  } else {
    return(NA)  # Unsupported file type
  }
}


```

```{r}

# Function to flag whether the keywords appear in the text
keyword_check <- function(file_path, keywords) {
  
  # Extract text and collapse into one string
  text <- extract_text(file_path) %>% paste(collapse = " ")  
  
  # Check for keyword matches 
  matches <- map_dfr(keywords, function(keyword){
    data.frame(
      "keyword" = keyword,
      "found" = str_detect(text, fixed(keyword, ignore_case = TRUE)))})
  
  # Return it as a table
  return(
    bind_cols(
      data.frame(proposal_name = basename(file_path)),
      matches
      ))
}
```

```{r}

# Function to count keyword occurrences in a file
count_keywords <- function(file_path, keywords) {
  
  # Extract text and collapse into one string
  text <- extract_text(file_path) %>% paste(collapse = " ")  
  
  # Check for keyword matches 
  matches <- map_dfr(keywords, function(keyword){
    data.frame(
      "keyword" = keyword,
      "count" = str_count(text, fixed(keyword, ignore_case = TRUE)))})
  
  # Return it as a table
  return(
    bind_cols(
      data.frame(proposal_name = basename(file_path)),
      matches
      ))
  
}

```

## Test Document: NASA_Peake_SciAct Extension.pdf

```{r}
# Check a pdf
keyword_check(
  pending_proposals$GEO_Tokunaga_OSW.pdf, 
  keywords = nsf_keywords) %>% 
  filter(found)

# check a docx
keyword_check(
  awarded_proposals$`EDA_Grimes_Build to Scale Capital Challenge.docx`,
  keywords = nsf_keywords)  %>% 
  filter(found)


```

```{r}
# Check a pdf
count_keywords(
  pending_proposals$GEO_Tokunaga_OSW.pdf, 
  keywords = nsf_keywords) %>% 
  filter(count > 0)

# check a docx
count_keywords(
  awarded_proposals$`EDA_Grimes_Build to Scale Capital Challenge.docx`,
  keywords = nsf_keywords) %>% 
  filter(count > 0)
```

### Process All Proposals

Using those functions we should be able to loop over all of the files and extract what we need:

```{r}
# Apply function to all pending proposals
pending_pdf_matches <- map_dfr(
  .x = pending_proposals, 
  .f = ~count_keywords(
    file_path = .x, 
    keywords = nsf_keywords)) %>% 
  mutate(status = "pending", .before = "keyword") 

# Apply function to all awarded proposals
awarded_pdf_matches <- map_dfr(
  .x = awarded_proposals, 
  .f = ~count_keywords(
    file_path = .x, 
    keywords = nsf_keywords)) %>% 
  mutate(status = "awarded", .before = "keyword") 


# Combine them:
proposal_keyword_counts <- bind_rows(awarded_pdf_matches, pending_pdf_matches)

```

## Results: Flagged Proposals

```{r}

proposal_matches <- proposal_keyword_counts %>% 
  filter(count > 0) %>% 
  distinct(proposal_name, status,  keyword, count) %>% 
  arrange(status, proposal_name, desc(count))


gt::gt(proposal_matches)
```

Most common flags

```{r}
proposal_keyword_counts %>% 
  group_by(keyword) %>% 
  summarise(total_counts = sum(count)) %>% 
  mutate(keyword = fct_reorder(keyword, total_counts, .fun = median)) %>% 
  ggplot(aes(y = keyword, x = total_counts)) +
  geom_col() +
  labs(x = "Times Flagged")
```

## Results: No Flags

We have three proposals that passed with no flags.

```{r}
unflagged_proposals <-  proposal_keyword_counts %>% 
  group_by(proposal_name, status) %>% 
  summarise(flag_total = sum(count),
            .groups = "drop") %>% 
  filter(flag_total ==  0) %>% 
  distinct(proposal_name, status, flag_total) %>% 
  arrange(status, proposal_name)


gt::gt(unflagged_proposals)
```

### Save

```{r}
write_csv(
  proposal_keyword_counts,# %>% filter(count > 0),
  here::here("local_data/2025_Proposal_RedFlag_Counts.csv")
)
```

# Categorized Results

In the

```{r}
# Prepare list to go through the categories:
keyword_list <- list(
  "NSF" = nsf_keywords,
  "Social Justice" = social_justice_keywords,
  "Environmental Justice" = env_justice_keywords,
  "Gender" = gender_keywords,
  "Race" = race_keywords,
  "Status" = status_keywords
)

# Run Them All
categorical_matches <- map_dfr(
  .x = keyword_list,
  .f = function(keywords){
    
    # Apply function to all pending proposals
    pendings <- map_dfr(
      .x = pending_proposals, 
      .f = ~count_keywords(
        file_path = .x, 
        keywords = keywords)) %>% 
      mutate(status = "pending", .before = "keyword") 
    
    # Apply function to all awarded proposals
    awardeds <- map_dfr(
      .x = awarded_proposals, 
      .f = ~count_keywords(
        file_path = .x, 
        keywords = keywords)) %>% 
      mutate(status = "awarded", .before = "keyword") 
    
    # Combine them:
    bind_rows(awardeds, pendings)
    
    },  .id = "DEIJ Category")


```

```{r}
#| fig.height = 10

categorical_matches %>% 
    group_by(`DEIJ Category`, keyword) %>% 
    summarise(total_counts = sum(count),
              .groups = "drop") %>%
    filter(total_counts > 0) %>% 
    mutate(
      keyword = tolower(keyword),
      keyword = fct_reorder(keyword, total_counts, .fun = median)) %>% 
    ggplot(aes(y = keyword, x = total_counts)) +
    geom_col() +
    #facet_wrap(~`DEIJ Category`, scales = "free") +
    facet_grid(`DEIJ Category`~., space = "free", scales = "free") +
  theme(axis.text = element_text(size = 8),
        strip.text.y = element_text(angle = 0)) +
    labs(x = "Times Flagged",
         title = "Keyword Flags in Awarded and Pending Proposals")

```
